Location of Tuna farms

### 2021-02-09 marine/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
finished adding data quality markers to all species groups. Now I need to summarize

```{r}
library(raster)
library(tidyverse)
library(stringr)
library(rgdal)
library(PBSmapping)
library(maptools)
library(sf)
library(lwgeom)
library(data.table)
library(here)
library(mapview)
library(janitor)

@@

Source: 
Aquaculture Stewardship Council Data Mapping Study, n.d. . Aquaculture Stewardship Council. [Accessed November 11, 2020] 
https://gis.asc-aqua.org/arcgis_app/

# get iso3c codes
iso <-   data.frame(iso3c = countrycode(ASC_shrimp$crt_cnt, origin = 'country.name', destination = 'iso3c'))

@@

```{r}
farms_bra <- data.frame(lat=c(-0.952238, -2.365963, -2.859201, -3.646201, -5.100375,  -7.089602, -8.115310, -9.700209, -10.991527, -13.046432, -25.535885, -27.505551),
                        lon=c(-48.466718, -44.263791, -41.551117, -38.627546, -35.667111, -34.818058, -34.840892, -35.739681, -37.030238, -38.515139, -48.268714, -48.393581),
                        area_ha = c(70, 64, 425, 982, 1752, 420, 670, 20, 47, 1510, 50, 200)) %>%
  mutate(iso3c = "BRA")

@@

```{r}
farms_brn <- data.frame(lat=c(4.716865, 4.722253, 4.742089, 4.761099, 4.781321, 4.970718),
                        lon=c(114.535353, 114.541318, 114.574539, 114.610558, 114.607222, 115.043816),
                        area_ha = c(14, 40, 92, 0.4, 200, 51.471511)) %>%
  mutate(iso3c = "BRN")

@@

# Cambodia 
 - There is a table in here that has potential. We will just place a point on the coast for each of these coastal places, and use the area noted in the paper later if needed. If the province is not coastal, it will not be placed on the map: https://clarklabs.org/wp-content/uploads/2019/01/Aquaculture-and-Coastal-Habitats-Report-No1.docx.pdf

@@

```{r}
farms_khm <- data.frame(lat=c(10.559329, 10.449929, 11.740932, 10.743017),
                        lon=c(104.213349, 104.404934, 102.898284, 103.653332),
                        area_ha = c(1516, 459, 26762, 6388)) %>%
  mutate(iso3c = "KHM")

@@

farms_cri_final <- farms_cri %>%
  mutate(iso3c = "CRI")

@@

```{r}
farms_cub <- data.frame(lat=c(19.841789, 20.047065),
                        lon=c(-77.737212, -77.593449),
                        area_ha = c(NA, NA)) %>%
  mutate(iso3c = "CUB")

@@

```{r}
farms_slv <- data.frame(lat=c(13.336985, 13.354459),
                        lon=c(-89.014470, -87.863771),
                        area_ha = c(8.2, 50)) %>%
  mutate(iso3c = "SLV")

@@

farms_irn <- data.frame(do.call(rbind, st_geometry(irn_pts_latlon))) 
names(farms_irn) <- c("lon", "lat")
farms_irn <- farms_irn %>%
  mutate(iso3c="IRN")

@@

```{r}
farms_jpn <- data.frame(lat=c(31.182129),
                        lon=c(130.604815),
                        area_ha = c(NA)) %>%
  mutate(iso3c = "JPN")

@@

```{r}
farms_kor <- data.frame(lat=c(36.752683),
                        lon=c(126.150252),
                        area_ha = c(672)) %>%
  mutate(iso3c = "KOR")

write_csv(farms_kor, here("aquaculture/marine/shrimp/shrimp_farms/data/farm_sites/farms_kor.csv"))

@@

Now lets map the farms 
```{r}
farms_mys <- data.frame(lat=c(6.433288, 2.108604, 1.676758, 3.018320, 5.674088, 4.984545, 5.596019, 2.197050, 3.888025, 3.663462, 3.203638),
                        lon=c(99.826952, 102.463536, 110.210032, 103.430156, 102.721589, 103.328932, 102.826214, 111.183470, 100.704595, 100.975557, 103.446051),
                        area_ha =mys_area) %>%
  mutate(iso3c = "MYS")

@@

```{r}
farms_mmr <- data.frame(lat=c(20.117197, 15.967665, 16.441903, 16.100756, 13.436424),
                        lon=c(92.884433, 94.337465, 96.371311, 97.581799, 98.323120),
                        area_ha = c(62941.972, 13505.574, 2992.246, NA, NA )) %>%
  mutate(iso3c = "MMR")

@@

farms_phl_final <- farms_phl %>%
  mutate(iso3c = "PHL") %>%
  mutate(area_ha = 13.35)

@@

```{r}
farms_sau <- data.frame(lat=c(20.287253, 17.806544),
                        lon=c(40.030864, 41.897791),
                        area_ha = c(7189, 206), 
                        prod = c(35000, 3000)) %>%
  mutate(iso3c = "SAU")

@@

farms_all_lka <- rbind(farms_bat_lka_final, farms_put_lka_final) %>%
  dplyr::mutate(iso3c = "LKA")

@@

 - It is unclear how many farms are in Taiwan. I will randomly place the farms along the coast.

@@

@@

gadm <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/manipulated_data/GADM36/gadm36molcountries_simp.shp")

 TWN_shp <- gadm %>%
  filter(GID_0 == "TWN") %>%
  st_transform(., food_crs) %>%
  mutate(Region = 1)
 mapview(TWN_shp)

st_write(TWN_shp, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.shp")

twn_reg_ras <- fasterize::fasterize(TWN_shp, fake_raster, fun = "sum")

plot(fake_raster)
plot(twn_reg_ras)

writeRaster(twn_reg_ras, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")

twn_reg_ras <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")

twn_spatial <- as(TWN_shp, "Spatial")

twn_coast <- rasterize(twn_spatial, twn_reg_ras, getCover = TRUE)

plot(twn_coast)
cellStats(twn_coast, "sum") #464.63

# filter to include >0 <1, o.w. NA

twn_coast_df <- as.data.frame(twn_coast, xy=TRUE) %>%
  dplyr::filter(layer <1 & layer >0) %>% ## filter out anything not on taiwan coast
  mutate(iso3c = "TWN") %>%
  dplyr::select(lon=x, lat=y, iso3c)

farms_twn <-  st_as_sf(twn_coast_df, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

write_csv(twn_coast_df, here::here("marine/shrimp/shrimp_farms/data/farm_sites/farms_twn.csv"))

twn <- read_csv(here::here("marine/shrimp/shrimp_farms/data/farm_sites/farms_twn.csv"))
farms_twn <-  st_as_sf(twn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_twn)
```

@@

```{r}
farms_usa <- data.frame(lat=c(28.709786, 28.731171, 28.369096, 26.323330, 26.149413, 30.403144, 21.957597,  29.859915, 26.602097, 24.972378),
                        lon=c(-96.209726, -96.203732, -96.813910, -97.452599, -97.322755, -88.254304, -159.669555, -85.287438, -82.113475, -80.555590),
                        area_ha = c(159.4461, 80, 40, 445, 182, NA, 104, 22, 3, 0.88)) %>%
  mutate(iso3c = "USA")

@@

write.csv(all_farms, here::here("marine/shrimp/shrimp_farms/data/global_shrimp_farm_lat_lon.csv"), row.names = FALSE)

>>>>

```{r}
library(raster)
library(tidyverse)
library(stringr)
library(rgdal)
library(PBSmapping)
library(maptools)
library(sf)
library(lwgeom)
library(data.table)
library(here)
library(mapview)
library(janitor)
library(rnaturalearth)
library(spatialEco)

@@

Source: 
Aquaculture Stewardship Council Data Mapping Study, n.d. Aquaculture Stewardship Council. [Accessed November 11, 2020] 
https://gis.asc-aqua.org/arcgis_app/

```{r}
library(countrycode)
# get iso3c codes
iso <-   data.frame(iso3c = countrycode(ASC_shrimp$crt_cnt, origin = 'country.name', destination = 'iso3c'))

@@

```{r}
farms_bra <- data.frame(lat=c(-0.952238, -2.365963, -2.859201, -3.646201, -5.100375,  -7.089602, -8.115310, -9.700209, -10.991527, -13.046432, -25.535885, -27.505551),
                        lon=c(-48.466718, -44.263791, -41.551117, -38.627546, -35.667111, -34.818058, -34.840892, -35.739681, -37.030238, -38.515139, -48.268714, -48.393581),
                        area_ha = c(70, 64, 425, 982, 1752, 420, 670, 20, 47, 1510, 50, 200)) %>%
  mutate(iso3c = "BRA") %>%
  mutate(data_quality = 0.333)

@@

```{r}
farms_brn <- data.frame(lat=c(4.716865, 4.722253, 4.742089, 4.761099, 4.781321, 4.970718),
                        lon=c(114.535353, 114.541318, 114.574539, 114.610558, 114.607222, 115.043816),
                        area_ha = c(14, 40, 92, 0.4, 200, 51.471511)) %>%
  mutate(iso3c = "BRN") %>%
  mutate(data_quality = 0.667)

@@

# Cambodia 
 - There is a table in here. We will just place a point on the coast for each of these coastal places, and use the area noted in the paper later if needed. If the province is not coastal, it will not be placed on the map: https://clarklabs.org/wp-content/uploads/2019/01/Aquaculture-and-Coastal-Habitats-Report-No1.docx.pdf

@@

farms_khm <- data.frame(lat=c(10.554565566560438, 10.4453604331596, 11.7394298718815, 10.744571388081424),
                        lon=c(104.21523743679825, 104.404236625661, 102.8937349735425, 103.65371151346486),
                        area_ha = c(1516, 459, 26762, 6388)) %>%
  mutate(iso3c = "KHM") %>%
  mutate(data_quality = 0.333)

@@

farms_cri_final <- farms_cri %>%
  mutate(iso3c = "CRI") %>%
  mutate(data_quality = 0.333)

@@

```{r}
farms_cub <- data.frame(lat=c(19.841789, 20.047065),
                        lon=c(-77.737212, -77.593449),
                        area_ha = c(NA, NA)) %>%
  mutate(iso3c = "CUB") %>%
  mutate(data_quality = 0.667)

@@

```{r}
farms_slv <- data.frame(lat=c(13.336985, 13.354459),
                        lon=c(-89.014470, -87.863771),
                        area_ha = c(8.2, 50)) %>%
  mutate(iso3c = "SLV") %>%
  mutate(data_quality = 0.333)

@@

farms_irn <- data.frame(do.call(rbind, st_geometry(irn_pts_latlon))) 
names(farms_irn) <- c("lon", "lat")
farms_irn <- farms_irn %>%
  mutate(iso3c="IRN") %>%
  mutate(data_quality = 0.667)

@@

```{r}
farms_jpn <- data.frame(lat=c(31.182129),
                        lon=c(130.604815),
                        area_ha = c(NA)) %>%
  mutate(iso3c = "JPN") %>%
  mutate(data_quality = 0.0)

@@

```{r}
farms_kor <- data.frame(lat=c(36.752683),
                        lon=c(126.150252),
                        area_ha = c(672)) %>%
  mutate(iso3c = "KOR") %>% 
  mutate(data_quality = 0.0)

write_csv(farms_kor, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_kor.csv"))

@@

Now lets map the farms 
```{r}
farms_mys <- data.frame(lat=c(6.433288, 2.108604, 1.676758, 3.018320, 5.674088, 4.984545, 5.596019, 2.197050, 3.888025, 3.663462, 3.203638),
                        lon=c(99.826952, 102.463536, 110.210032, 103.430156, 102.721589, 103.328932, 102.826214, 111.183470, 100.704595, 100.975557, 103.446051),
                        area_ha =mys_area) %>%
  mutate(iso3c = "MYS") %>%
  mutate(data_quality = 0.333)

@@

```{r}
farms_mmr <- data.frame(lat=c(20.117197, 15.967665, 16.441903, 16.100756, 13.436424),
                        lon=c(92.884433, 94.337465, 96.371311, 97.581799, 98.323120),
                        area_ha = c(62941.972, 13505.574, 2992.246, NA, NA )) %>%
  mutate(iso3c = "MMR") %>%
  mutate(data_quality = 0.333)

@@

farms_phl_final <- farms_phl %>%
  mutate(iso3c = "PHL") %>%
  mutate(area_ha = 13.35) %>%
  mutate(data_quality = 0.333)

@@

```{r}
farms_sau <- data.frame(lat=c(20.287253, 17.806544),
                        lon=c(40.030864, 41.897791),
                        area_ha = c(7189, 206), 
                        prod = c(35000, 3000)) %>%
  mutate(iso3c = "SAU") %>%
  mutate(data_quality = 0.667)

@@

farms_all_lka <- rbind(farms_bat_lka_final, farms_put_lka_final) %>%
  dplyr::mutate(iso3c = "LKA") %>%
  mutate(data_quality = 0.333)

@@

 - It is unclear how many farms are in Taiwan. I will randomly place a farm on the coast.

@@

farms_twn <- data.frame(lat = c(22.33895226304863),
                        lon = c(120.60403687783123)) %>%
  mutate(iso3c = "TWN") %>%
  mutate(data_quality = 0.0)

write_csv(farms_twn, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_twn.csv"))

## visualize it 
farms_twn <-  st_as_sf(farms_twn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

@@

# gadm <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/manipulated_data/GADM36/gadm36molcountries_simp.shp")
# 
#  TWN_shp <- gadm %>%
#   filter(GID_0 == "TWN") %>%
#   st_transform(., food_crs) %>%
#   mutate(Region = 1)
#  mapview(TWN_shp)
# 
# st_write(TWN_shp, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.shp")
# 
# twn_reg_ras <- fasterize::fasterize(TWN_shp, fake_raster, fun = "sum")
# 
# 
# plot(fake_raster)
# plot(twn_reg_ras)
# 
# writeRaster(twn_reg_ras, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")
# 
# 
# twn_reg_ras <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")
# 
# twn_spatial <- as(TWN_shp, "Spatial")
# 
# twn_coast <- rasterize(twn_spatial, twn_reg_ras, getCover = TRUE)
# 
# plot(twn_coast)
# cellStats(twn_coast, "sum") #464.63
# 
# # filter to include >0 <1, o.w. NA
# 
# twn_coast_df <- as.data.frame(twn_coast, xy=TRUE) %>%
#   dplyr::filter(layer <1 & layer >0) %>% ## filter out anything not on taiwan coast
#   mutate(iso3c = "TWN") %>%
#   dplyr::select(lon=x, lat=y, iso3c)
# 
# farms_twn <-  st_as_sf(twn_coast_df, coords = c("lon", "lat"), 
#                  crs = crs(gadm_latlon), agr = "constant")
# 
# mapview(farms_twn)
# 
# 
# write_csv(twn_coast_df, here::here("marine/shrimp/shrimp_farms/data/farm_sites/farms_twn.csv"))
# 
# 
# twn <- read_csv(here::here("marine/shrimp/shrimp_farms/data/farm_sites/farms_twn.csv"))
# farms_twn <-  st_as_sf(twn, coords = c("lon", "lat"), 
#                  crs = crs(gadm_latlon), agr = "constant")
# 
# mapview(farms_twn)
```

@@

```{r}
farms_usa <- data.frame(lat=c(28.709786, 28.731171, 28.369096, 26.323330, 26.149413, 30.403144, 21.957597,  29.859915, 26.602097, 24.972378),
                        lon=c(-96.209726, -96.203732, -96.813910, -97.452599, -97.322755, -88.254304, -159.669555, -85.287438, -82.113475, -80.555590),
                        area_ha = c(159.4461, 80, 40, 445, 182, NA, 104, 22, 3, 0.88)) %>%
  mutate(iso3c = "USA") %>%
  mutate(data_quality = 0.667)

@@

all_farms_1 <- all_farms %>%
  dplyr::select(-data_quality)

write.csv(all_farms_1, here::here("marine/shrimp/shrimp_farms/data/global_shrimp_farm_lat_lon.csv"), row.names = FALSE)
write.csv(all_farms, here::here("marine/shrimp/shrimp_farms/data/global_shrimp_farm_lat_lon_data_quality.csv"), row.names = FALSE)

### 2021-02-09 marine/tuna/tuna_farms/STEP2_tuna_farm_locations.Rmd
finished adding data quality markers to all species groups. Now I need to summarize

farms_eu_final <- cbind(farms_eu, eu_countries) %>%
  dplyr::select(-geometry) %>%
  mutate(iso3c = case_when(
    COUNTRY == "Spain" ~ "ESP",
    COUNTRY == "Malta" ~ "MLT"
  )) %>%
  dplyr::select(-COUNTRY)

@@

med_countries <- france_aqua %>%
  dplyr::mutate(country = sub("_.*", "", Name)) %>%
  dplyr::mutate(country = sub(" fishpen A", "", country))

@@

## We need to filter for just the appropriate species of finfish aquaculture, France, Israel

@@

mapview(med_tuna)

@@

farms_med <- data.frame(do.call(rbind, st_geometry(med_pts_latlon)))
names(farms_med) <- c("lon", "lat")
farms_med <- farms_med %>%
  cbind(countries) %>%
  mutate(iso3c = ifelse(country == "Croatia", "HRV", "TUR")) %>%
  dplyr::select(-country, -geometry)

@@

```{r}
south_au <- read_csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/Australia/south_au_leases.csv"))

@@

## unlist the list to get our coordinates 
lat_lon_final <- coords_list %>%
    bind_rows() %>%
  mutate(lat = -lat) %>% ## change lat to have a negative in front of it (because it S)
  mutate(iso3c = "AUS")
## now that we have coordinates, place them on a map and save

@@

farms_jpn_final <- farms_jpn %>%
  mutate(iso3c = "JPN")

@@

farms_mex <- data.frame(lat = c(31.972882899404116, 31.96836856413186, 31.963417102445995, 31.95861101663323, 31.955698114940013, 31.952930772763118, 31.95030900327055, 31.945939221180044, 31.932974311561416, 31.929769220541903, 31.95016334721594, 31.959630510399904, 31.96764042474878),
                          lon = c(-116.81987407899483, -116.8094027351974, -116.80339458711688, -116.7956698252991, -116.79343822744065, -116.79000499996607, -116.78777340210759, -116.78193691540082, -116.77575710594658, -116.77180889435084, -116.77060726473474, -116.78262356089573, -116.79395321156183), 
                          iso3c = "MEX")

@@

write.csv(all_farms, here::here("marine/tuna/tuna_farms/data/global_tuna_farm_lat_lon.csv"), row.names = FALSE)

>>>>

farms_eu_final <- cbind(farms_eu, eu_countries) %>%
  dplyr::select(-geometry) %>%
  mutate(iso3c = case_when(
    COUNTRY == "Spain" ~ "ESP",
    COUNTRY == "Malta" ~ "MLT"
  )) %>%
  dplyr::select(-COUNTRY) %>%
  mutate(data_quality = 1.0)

@@

med_countries <- med_aqua %>%
  dplyr::mutate(country = sub("_.*", "", Name)) %>%
  dplyr::mutate(country = sub(" fishpen A", "", country))

@@

## We need to filter for just the appropriate countries (that we don't already have): Croatia, Turkey

@@

mapview(med_tuna)
mapview(med_aqua)

@@

farms_med <- data.frame(do.call(rbind, st_geometry(med_pts_latlon)))
names(farms_med) <- c("lon", "lat")
farms_med <- farms_med %>%
  cbind(countries) %>%
  mutate(iso3c = ifelse(country == "Croatia", "HRV", "TUR")) %>%
  dplyr::select(-country, -geometry) %>%
  mutate(data_quality = 0.667)

@@

```{r}
south_au <- read_csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/Australia/tuna/south_au_leases.csv"))

@@

## unlist the list to get our coordinates 
lat_lon_final <- coords_list %>%
    bind_rows() %>%
  mutate(lat = -lat) %>% ## change lat to have a negative in front of it (because it S)
  mutate(iso3c = "AUS") %>%
  mutate(data_quality = 1.0)
## now that we have coordinates, place them on a map and save

@@

farms_jpn_final <- farms_jpn %>%
  mutate(iso3c = "JPN") %>%
  mutate(data_quality = 0.333)

@@

farms_mex <- data.frame(lat = c(31.972882899404116, 31.96836856413186, 31.963417102445995, 31.95861101663323, 31.955698114940013, 31.952930772763118, 31.95030900327055, 31.945939221180044, 31.932974311561416, 31.929769220541903, 31.95016334721594, 31.959630510399904, 31.96764042474878),
                          lon = c(-116.81987407899483, -116.8094027351974, -116.80339458711688, -116.7956698252991, -116.79343822744065, -116.79000499996607, -116.78777340210759, -116.78193691540082, -116.77575710594658, -116.77180889435084, -116.77060726473474, -116.78262356089573, -116.79395321156183), 
                          iso3c = "MEX") %>%
  mutate(data_quality = 0.667)

@@

write.csv(all_farms_1, here::here("marine/tuna/tuna_farms/data/global_tuna_farm_lat_lon.csv"), row.names = FALSE)

write.csv(all_farms, here::here("marine/tuna/tuna_farms/data/global_tuna_farm_lat_lon_data_quality.csv"), row.names = FALSE)
